---
title: Verification of power-law with poweRlaw package
author: Jiho Yeo
date: '2019-08-09'
slug: verification-of-power-law-with-powerlaw-package
categories:
  - R
  - Network sience
  - Statistics
  - Study
tags:
  - scale-free
  - network science
  - power-law
subtitle: ''
summary: ''
authors: []
lastmod: '2019-08-09T19:01:45+09:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

이 포스팅에서는 R의 `poweRlaw` package를 이용해서 어떻게 power-law coefficient를 도출하고, statistical significance를 도출하는지를 살펴보고자 한다. 

이론적 고찰을 위해  
[Fitting heavy tailed distributions: the poweRlaw package](https://arxiv.org/abs/1407.3492)
[Power-Law Distributions in Empirical Data](https://epubs.siam.org/doi/abs/10.1137/070710111)  
를 참고하였고 poweRlaw package의 Examples를 [이곳](https://cran.r-project.org/web/packages/poweRlaw/vignettes/b_powerlaw_examples.pdf)에서 참고하였다. 

## **






## **실습**

이곳에 있는 코드의 대부분은 [이곳](https://cran.r-project.org/web/packages/poweRlaw/vignettes/b_powerlaw_examples.pdf)에서 참고하였다.

### 1. Discrete data: The Moby Dick data set

The Moby Dick data set contains the frequency of unique words in the novel Moby Dick by Herman Melville. 
This data set can be downloaded from http://tuvalu.santafe.edu/∼aaronc/powerlaws/data.htm
or loaded directly

```{r}
library("poweRlaw")
data("moby", package="poweRlaw")
```

To fit a discrete power law to this data, we use the displ constructor

```{r}
m_pl <- displ$new(moby)
```

We estimate the lower threshold via

```{r}
est <- estimate_xmin(m_pl)
```

and update the power law object

```{r}
m_pl$setXmin(est)
```

For a given value xmin, the scaling parameter is estimated by numerically optimising the loglikelihood. 
The optimiser is initialised using the analytical MLE

$\hat{\alpha} = 1 + n[\sum_{i=1}^n log({x_i\over x_{min}-0.5})]^{-1}$

```{r}
est
```

This yields a threshold estimate of $x_min$ = 7 and scaling parameter $\alpha$= 1.95

Alternatively, we could perform a parameter scan for each value of $x_min$

```{r}
estimate_xmin(m_pl, pars=seq(1.8, 2.3, 0.1))
```

To fit a discrete log-normal distribution, we follow a similar procedure, except we begin by creating a dislnorm object

```{r}
m_ln = dislnorm$new(moby)
est = estimate_xmin(m_ln)
est
```

which yields a lower threshold of xmin = 3 and parameters (−17.9, 4.87)  
the log-normal and power law distribution both provide reasonable fits to the data.

**Parameter uncertainty**

To get a handle on the uncertainty in the parameter estimates, we use a bootstrapping procedure, via the bootstrap function.

```{r eval=F, include=T}
## 5000 bootstraps using two cores
bs = bootstrap(m_pl, no_of_sims=5000, threads=2)
```

